Invariant Representations for Noisy Speech Recognition

### 2016-11-30 poster.tex
Prettify experiments section

            \begin{block}{{\Large Experiments on Aurora-4}}
                In order to evaluate the impact of our method on generalization to unseen noises,
                we performed 6 experiments with different set of seen noises. The networks are trained
                on clean data, with each noise condition added one-by-one in the following order: airport, babble, car, 
                restaurant, street, and train.

                Average performance of the baseline multi-condition and invariance model varying with the 
                number of noise conditions used for training. Average performance on seen versus 
                unseen noise conditions.
                Testing was performed on all wv1 conditions (Sennheiser microphone).
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_avg.pdf}
                \end{figure}
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
                \end{figure}
            \end{block}
        \end{column} % end of third column
    \end{columns}
\end{column}

>>>>

            \begin{block}{{\Large Experiments on Aurora-4}}
                \begin{itemize}
                    \item We performed 6 experiments with different set of seen noises. 
                    \item The networks are trained
                on clean data, with each noise condition added one-by-one in the following order: airport, babble, car, 
                restaurant, street, and train:
                    \begin{enumerate}
                        \item clean + airport
                        \item clean + airport + babble
                        \item \ldots
                    \end{enumerate}
                \end{itemize}

                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_avg.pdf}
                \end{figure}
                Average performance of the baseline multi-condition and invariance model varying with the 
                number of noise conditions used for training. 
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
                \end{figure}
                Average performance on seen versus 
                unseen noise conditions.
                Testing was performed on all wv1 conditions (Sennheiser microphone).
            \end{block}
        \end{column} % end of third column
    \end{columns}
\end{column}
